Using CopyKAT to identify tumor cells in Ewing sarcoma samples

### 2024-06-05 analyses/cell-type-ewings/template_notebooks/02-cellassign.Rmd
fix cellassign errors

```{r packages}
suppressPackageStartupMessages({
  # load required packages
  library(SingleCellExperiment)
  library(ggplot2)
})
```

@@

  caret::confusionMatrix(
    table(
      celltype_df$caret_cellassign_annotations, 
      celltype_df$caret_visser_annotations)
  ) 
} else {
  message("No endothelial cells were classified by `CellAssign`.")
}
```

@@

The last thing we will do here is run CellAssign using some of the same reference that we used when running CellAssign as part of scpca-nf. 
In particular, the majority of non-muscle cells (which we believe to be tumor cells) were identified as either Endothelial cells or Fibroblasts.
So we will use a reference that takes the markers for Endothelial cells and Fibroblasts from PanglaoDB and combines with the tumor markers.

>>>>

```{r packages}
suppressPackageStartupMessages({
  # load required packages
  library(SingleCellExperiment)
  library(ggplot2)
})

knitr::opts_chunk$set(
  dev = "jpeg"
)
```

@@

  if(all("Endothelial cells", "Other") %in% celltype_df$visser_cellassign_annotations &&
     all("Endothelial cells", "Other") %in% celltype_df$cellassign_celltype_annotation){
    caret::confusionMatrix(
      table(
        celltype_df$caret_cellassign_annotations, 
        celltype_df$caret_visser_annotations)
    )  
  }
} else {
  message("No endothelial cells were classified by `CellAssign`.")
}
```

@@

The last thing we will do here is run CellAssign using some of the same reference that we used when running CellAssign as part of `scpca-nf`. 
In particular, the majority of non-muscle cells (which we believe to be tumor cells) were identified as either Endothelial cells or Fibroblasts.
So we will use a reference that takes the markers for Endothelial cells and Fibroblasts from PanglaoDB and combines with the tumor markers.

### 2024-06-05 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd

---
title: "Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  no_ref_copykat_results: "copykat/no_reference"
  with_ref_copykat_results: "copykat/with_reference"
  reference_cell_file: ".reference-cells.tsv"
  results_dir: "annotate_tumor_cells_output"
---

@@

```{r packages}
suppressPackageStartupMessages({
  # load required packages
  library(SingleCellExperiment)
  library(ggplot2)
  library(copykat)
})
```

>>>>

---
title: "Using CopyKAT to identify tumor cells in Ewing sarcoma samples"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  no_ref_copykat_results: "copykat/no_reference"
  with_ref_copykat_results: "copykat/with_reference"
  reference_cell_file: ".reference-cells.tsv"
  results_dir: "annotate_tumor_cells_output"
---

@@

```{r packages}
suppressPackageStartupMessages({
  # load required packages
  library(SingleCellExperiment)
  library(ggplot2)
  library(copykat)
})

knitr::opts_chunk$set(
  dev = "jpeg"
)
```
